{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-09-08 wacv_for_review.tex
Final Edits - 8 Pages Paper

%%%%%%%%% TITLE
\title{{\it E}nKCF: Ensemble of Kernelized Correlation Filters for
  High-Speed, Object Tracking}

@@

One of the dominant frameworks for online, object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like any other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time \cite{henriques2015high}. This is primarily due to
the dilemma of stability-plasticity in updating appearance model,
where the appearance model will be overfitted to only the images used
to train, unless a compromise on the frequency of updating the model
is carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple of a correlation filter including
KCF on each frame.

@@

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area, translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area is tended to be noisy and less discriminative and adding color
information makes the feature vector for the translation filter,
$R_{t}^{L}$, more robust to noise and more discriminative. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. But,
this is not the case for the small area, translation filter,
$R_{t}^{S}$, because this translation filter does not contain much of
the background area around the target. Figure \ref{fig:Filters}(a)
shows an example of this translation filter. Lastly, we use both fHoG
and color-naming features again for the scale filter,
$R_{s}$. Although we are using the same feature representations for
the scale filter learning relatively smaller area just around the
target, the reason of using two feature sets is sightly different in
that the area to learn is too small for the fHoG to represent the area
well. In addition, the scale filter, explained earlier in the
algorithm \ref{alg:MKCF}, estimates the scale of a target by
correlating it with three candidate ROIs. This search may increase the
run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
practical, we use a smaller template size (i.e., 64$\times n$) for the
scale filter, $R_{s}$. The smaller template size does not degrade the
tracking performance neither because of 1) zero padding around the
target and 2) use of color feature.
\begin{comment}
The ROI considered by $R_{s}$ is resized to a smaller template
resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
This leads to less discriminative shape features. To reduce the noise
in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
scale by correlating the filter with three candidate ROIs as detailed
in alg.~\ref{alg:MKCF}.  This increases the complexity from
$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
reduce the number of operations, we assign a smaller template size to
$R_{s}$.  This does not degrade the tracking performance due to two
reasons: (1) zero padding around the target and (2) integration of
color features. This way, we keep the run-time complexity of the
$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of
$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
systems.

@@

{\it Burak: What you told me is purely empirical which is fine. But
  you'll have to tell the readers why we wanted to keep the run-time
  complexity of those filters same!}
\end{comment}
\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF is
designed to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.
\begin{comment}
{\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to lost spatial information this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction
capacity.  Their method first employs the third convolutional layer
features to estimate the response map. In the next stage, the KCF,
concentrating on the second convolutional layer features, is run to
update transition. The third KCF then works on the transition given by
the previous KCF and learns the first convolutional layer features to
update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it runs
multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
level of feature encodings with different KCFs. The translation
filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
area than the scale filter, $R_{s}$. Given this, we can assign deeper
feature encodings to $R_{s}$ as it learns less spatial information
than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
the fourth convolutional layer features ($26\times26\times128$) to
$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
activations of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. {\it Burak: I don't see any differenciation
  between conv222-VGG and conv224-VGG from the figure, at least labels
  of them.} We use the VGGNet since it provides higher spatial
resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to avoid distortion caused by FFT operation whereas $R_{s}$ is not filtered {\it Burak: What do you mean by ``not filtered''?} to avoid target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

@@

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $X_t$, represents a target's pixel
coordinates and its velocity, $X_t = \lbrace x, y, v_{x}, v_{y}
\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
centroid, $v_x$ and $v_y$ are the velocity estimated along the
$x$-axis and $y$-axis. The particle filter predicts, using a constant
velocity motion model, a target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update the state. The weight of a particle is
computed as
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j), 
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed {\it E}nKCF tracker and
its variants using the object tracking benchmark
datasets. Particularly, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.  We
first evaluate the performance of {\it E}nKCF with two hand-crafted
features, fHoG and color-naming.  With this tracker, we aim at
developing an object tracking algorithm that ``efficiently'' runs on
an embedded system, a drone, for example, in ``high speed,'' $\ge 30$
fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes,
e.g., abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Also, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets. Finally, we evaluate the
Deep{\it E}nKCF, {\it E}nKCF with deep features, on the UAV123 dataset
to observe how much gain we can achieve over hand-crafted features.

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed to address specific challenges in single, target
tracking problem. Thus each of them should have different values for
the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. Finally, the padding size for the correlation filters is tuned
to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
$R_{s}$. For our particle filter implementation, we empirically set
the number of particles to $1000$ to balance the run-time performance
and accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

@@

\begin{table*}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table*}

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column flipped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection method
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective, single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle tracking of object in fast motion and in
large camera motion. Specifically we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF with another vision of the UAV123 that
the original dataset was temporally down-sampled at $10$ fps and makes
the challenging original dataset, because of objects in fast motion
and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than the MUSTER
tracker.

>>>>

%%%%%%%%% TITLE
\title{{\it E}nKCF: Ensemble of Kernelized Correlation Filters for
  High-Speed Object Tracking}

@@

One of the dominant frameworks for online, object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like any other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time \cite{henriques2015high}. This is primarily due to
the dilemma of stability-plasticity in updating appearance model,
where the appearance model will be overfitted to only the images used
to train, unless a compromise on the frequency of updating the model
is carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple KCF on each frame.

@@

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area, translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area is tended to be noisy and less discriminative and adding color
information makes the feature vector for the translation filter,
$R_{t}^{L}$, more robust to noise and more discriminative. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. But,
this is not the case for the small area, translation filter,
$R_{t}^{S}$, because this translation filter does not contain much of
the background area around the target. Figure \ref{fig:Filters}(a)
shows an example of this translation filter. Lastly, we use both fHoG
and color-naming features again for the scale filter,
$R_{s}$. Although we are using the same feature representations for
the scale filter learning relatively smaller area just around the
target, the reason of using two feature sets is slightly different in
that the area to learn is too small for the fHoG to represent the area
well. In addition, the scale filter, explained earlier in the
algorithm \ref{alg:MKCF}, estimates the scale of a target by
correlating it with three candidate ROIs. This search may increase the
run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
practical, we use a smaller template size (i.e., 64$\times n$) for the
scale filter, $R_{s}$. The smaller template size does not degrade the
tracking performance neither because of 1) zero padding around the
target and 2) use of color feature.
\begin{comment}
The ROI considered by $R_{s}$ is resized to a smaller template
resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
This leads to less discriminative shape features. To reduce the noise
in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
scale by correlating the filter with three candidate ROIs as detailed
in alg.~\ref{alg:MKCF}.  This increases the complexity from
$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
reduce the number of operations, we assign a smaller template size to
$R_{s}$.  This does not degrade the tracking performance due to two
reasons: (1) zero padding around the target and (2) integration of
color features. This way, we keep the run-time complexity of the
$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of
$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
systems.

@@

{\it Burak: What you told me is purely empirical which is fine. But
  you'll have to tell the readers why we wanted to keep the run-time
  complexity of those filters same!}
\end{comment}

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF is
designed to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.
\begin{comment}
{\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to lost spatial information this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction
capacity.  Their method first employs the third convolutional layer
features to estimate the response map. In the next stage, the KCF,
concentrating on the second convolutional layer features, is run to
update transition. The third KCF then works on the transition given by
the previous KCF and learns the first convolutional layer features to
update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it runs
multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
level of feature encodings with different KCFs. The translation
filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
area than the scale filter, $R_{s}$. Given this, we can assign deeper
feature encodings to $R_{s}$ as it learns less spatial information
than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
the fourth convolutional layer features ($26\times26\times128$) to
$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
activations of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. The conv222 setting stands for the assignment of 
the activations of $2^{th}$, $2^{th}$ and $4^{th}$ convolutional layer features
of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet 
since it provides higher spatial resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to avoid distortion caused by FFT operation whereas $R_{s}$ does not, to avoid target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

@@

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $X_t$, represents a target's pixel
coordinates and its velocity, $X_t = \lbrace x, y, v_{x}, v_{y}
\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
centroid, $v_x$ and $v_y$ are the velocity estimated along the
$x$-axis and $y$-axis. The particle filter predicts, using a constant
velocity motion model, a target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update the state. The weight of a particle is
computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$,
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. 
%Alternatively one can
%also use the Euclidean distance of particles to the location of
%maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed {\it E}nKCF tracker and
its variants using the object tracking benchmark
datasets. Particularly, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.  We
first evaluate the performance of {\it E}nKCF with two hand-crafted
features, fHoG and color-naming.  With this tracker, we aim at
developing an object tracking algorithm that ``efficiently'' runs on
an embedded system, a drone, for example, in ``high speed,'' $\ge 30$
fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes,
e.g., abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Also, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets. Finally, we evaluate the
Deep{\it E}nKCF, {\it E}nKCF with deep features, on the UAV123 dataset
to observe how much gain we can achieve over hand-crafted features.

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed to address specific challenges in single, target
tracking problem. Thus each of them should have different values for
the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. Finally, the padding size for the correlation filters is tuned
to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
$R_{s}$. For our particle filter implementation, we empirically set
the number of particles to $1000$ to balance the run-time performance
and accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples}, ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a pre-defined
threshold.

@@

\begin{table*}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal. The '$*$' represents
  sequential approach where multiple KCFs are run in the given order in every frame as in LCT \cite{ma2015long}.}
\label{table:Comparison_to_LCT}
\end{table*}

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column flipped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection module
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective, single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle tracking of object in fast motion and in
large camera motion. Specifically, we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF with another vision of the UAV123 that
the original dataset was temporally down-sampled at $10$ fps and makes
the challenging original dataset, because of objects in fast motion
and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than MUSTER.

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board, embedded
system. To this end, we used two conventional features, fHoG and
color-naming for the {\it E}nKCF. At the same time, we observed that
the feature vectors learned from DNN have been used to improve the
performance of the trackers based on KCF \cite{ma2015hierarchical,
  danelljan2015convolutional}, and some of the single-board, embedded
systems have GPUs. We believe that the performance of the {\it E}nKCF
could be also improved with deep convolutional features trained on ImageNet dataset.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.
